3.9: Logarithmic Regression - R Practice

### 2019-11-30 content/r/21-r-practice.Rmd
Finalize HW 5 question page, fix 21 r practice
Add problem set 5 rmd
Add R Practice 21 answers

@@

Run an $F$-test to check if a nonlinear model is appropriate. Your null hypothesis is $H_0: $\beta_2+\beta_3=0$ from the regression in pert (h). The command is `linearHypothesis(reg_name, c("var1", "var2"))` where `reg_name` is the name of the `lm` object you saved your regression in, and `var1` and `var2` (or more) in quotes are the names of the variables you are testing. This function requires (installing and) loading the "`car`" package (additional regression tools).

@@

>>>>

Answers:
- [<i class="fas fa-external-link-square-alt"></i> `Answer Key (html)`](/r/19-r-practice-answers.html)
- [<i class="fab fa-markdown"></i> `Answer Key (markdown)`](/r/19-r-practice-answers.Rmd)

@@

Run an $F$-test to check if a nonlinear model is appropriate. Your null hypothesis is $H_0: \beta_2=\beta_3=0$ from the regression in pert (h). The command is `linearHypothesis(reg_name, c("var1", "var2"))` where `reg_name` is the name of the `lm` object you saved your regression in, and `var1` and `var2` (or more) in quotes are the names of the variables you are testing. This function requires (installing and) loading the "`car`" package (additional regression tools).

@@

# Question 9
Make a regression output table with `huxtable` of your regressions in Questions 2, 3, 4, 6a, 6b, 6c, 7 and 8.
